Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-03 manuscript/manuscript.Rmd

In Figure \@ref(fig:flood-zone-pca), we plot the learned embeddings for `flood_zone` in Model 3 on the coordinate
system defined by the first two principle components. (TODO: add commentary after update pic)

```{r flood-zone-pca, echo = FALSE, fig.cap="Flood zone PCA", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/flood_zone_pca.png")
```

@@

While t-SNE is a powerful visualization technique, there are a few points the modeler should be mindful of in practice.
First, the resulting plot can be very sensitive to the perplexity hyperparameter. 
In Figures \@ref(fig:flood-zone-tsne), we display the t-SNE of the learned embeddings for `flood_zone` in
Model 3 with various perplexity settings. (TODO: add more commentary).

>>>>

In Figure \@ref(fig:flood-zone-pca), we plot the learned embeddings for `flood_zone` in Model 3 on the coordinate
system defined by the first two principle components. In our case, however, we are not able to identify discernable
clusters in the plot. From inspecting the matrix decomposition results, we see that the cumulative proportion of
variance for the first two principal components are just 0.18, which may suggest that perhaps PCA is not the most
appropriate dimensionality reduction technique in this case.

```{r flood-zone-pca, echo = FALSE, fig.cap="Flood zone PCA", out.width = "50%", fig.align = "center"}
knitr::include_graphics("images/flood_zone_pca.png")
```

@@

While t-SNE is a powerful visualization technique, there are a few points the modeler should be mindful of in practice.
We refer the reader to @wattenberg2016how for a more thorough discussion, but stress here that the resulting plot can
be very sensitive to the perplexity hyperparameter. In addition, for our use case, which is to explore the
learned embeddings, we have fewer data points than most other applications in the literature. Accordingly, our
reaosnable range of hyperparameter values need to be adjusted down.
In Figures \@ref(fig:flood-zone-tsne), we display the t-SNE of the learned embeddings for `flood_zone` in
Model 3 with various perplexity settings: 0.1, 0.5, 1.0, and 10; the learning rate and the number of steps are fixed at
100 and 10,000, respectively, for all plots. In the first three plots, we can see the semblance of clusters forming. In
particular, flood zone D appears in its own cluster, which implies it is far away from other levels in the embedding
space. When the perplexity is set to 10 (and beyond), however, we lose the geometric properties.
